---
title: "The Effect of Probiotics on Child-Stunting and Development"
author: "Sasha Aibara"
date: "12/16/2021"
output: html_document
---

```{r setup, echo=FALSE, include=FALSE, warning=FALSE}

#==============================================================================
# Simulate data to estimate a treatment effect in an RCT
#==============================================================================

#==========
#Set Up
#==========

# Clear the working space
  rm(list = ls())
  
  library(tidyverse) # data wrangling and aggregations
  library(sandwich)
  library(stargazer)
  library(dplyr)
  library(scales)
  library(fmsb)
  library(ggradar)

# turn off scientific notation except for big numbers
options(scipen = 9)
# function to calculate corrected SEs for regression 
cse <- function(reg) {
  rob = sqrt(diag(vcovHC(reg, type = "HC1")))
  return(rob)
}

```


```{r data, warning=FALSE, echo=FALSE}

#===========

# Simulate data
  set.seed(1234)
  N =1000

# Create a variable "comply" for whether a person is "complier" (in treatment group they
# will comply with treatment, in control group interpreted as spillover from treatment.
# Here set 10% of all people to be non-compliers.
  
# Add variables for child's age, gender, diarrhea occurrence, village id, mom's height, dad's height, pre-existing medical conditions, and wealth index 
# Variable description/units: age of child (measured in years), gender of child (male or female, binomial), number of diarrhea episodes per year (measured on scale from 1-5 (more than 2 is unhealthy)), village_id (which village each child is from), educ_mom (years, how many years of education the mom has from 1-7), med_cond (yes or no, binomial), height (inches),
#wealth_index (scale from 1-5)
  
  df <- data.frame(comply=sample(c(0, 1), N,replace=TRUE, prob=c(.1, .9)),
                  male= rbinom(N,1,.45),
                  age=sample(1:5, N, replace = TRUE), 
                  diarrhea=sample(1:5, N, replace = TRUE),
                  village_id=sample(1:20, N, replace=TRUE), 
                  educ_mom=sample(1:7, N, replace=TRUE),
                  med_cond=rbinom(N,1,.45),
                  wealth_index=sample(1:5, N, replace=TRUE, prob=c(.3,.3,.2,.1,.1)),
                  mom_height=sample(61:66, N, replace=TRUE),
                  dad_height=sample(66:72, N, replace=TRUE),
                  post=0)  
  
 # Create a variable "treat" that  will be indicator for treatment and control groups.
  df<-df %>% mutate(treat=
    ifelse(10 >= village_id, 1, 
    ifelse(11<= village_id & village_id <= 20, 0, NA)))
  
# Add a variable "id" to identify each participant. 
  df <- df %>% mutate(id=row_number())
 
#Define a variable "height" (height-for-age) measured in inches. 
  df<-df %>%mutate(height=
    ifelse(age==1, sample(25:30, n(), replace=TRUE),
    ifelse(age==2, sample(31:34, n(), replace=TRUE),
    ifelse(age==3, sample(35:39, n(), replace=TRUE),
    ifelse(age==4, sample(37:40, n(), replace=TRUE),
    ifelse(age==5, sample(39:43, n(), replace=TRUE), NA))))))
  
#Define a variable "weight" (weight-for-age) measured in pounds. 
  
  df<-df %>% mutate(weight=
    ifelse(age==1, sample(15:20, n(), replace=TRUE),
    ifelse(age==2, sample(19:26, n(), replace=TRUE),
    ifelse(age==3, sample(24:30, n(), replace=TRUE),
    ifelse(age==4, sample(28:35, n(), replace=TRUE),
    ifelse(age==5, sample(31:40, n(), replace=TRUE), NA))))))
  
#Define a variable "upper_arm" for upper-arm circumference, measured in inches (indicator for malnutrition). 
  
  df<-df %>% mutate(upper_arm=
    ifelse(age==1, sample(4.7:5.5, n(), replace=TRUE),
    ifelse(age==2, sample(5:6, n(), replace=TRUE),
    ifelse(age==3, sample(5.2:6.1, n(), replace=TRUE),
    ifelse(age==4, sample(5.3:6.5, n(), replace=TRUE),
    ifelse(age==5, sample(5.5:6.6, n(), replace=TRUE), NA))))))
  
  
# Now copy the data set and change the variable post=1 (observe after treatment).
  df2 <- df %>% mutate(post=1)
# Then append the two data frames so now have a "long" dataset (each id observed twice)
  df <- rbind(df, df2)
  rm(df2)
  
              
# Define a variable treat_effect that will be the simple treatment effect
df <- df %>% mutate(treat_effect_h=
    ifelse(treat==1 & comply==1, 2,
    ifelse(treat==1 & comply==0, 1,
    ifelse(treat==0 & comply==1, .5,
    ifelse(treat==0 & comply==0, .5, NA)))))

df <- df %>% mutate(treat_effect_w=
    ifelse(treat==1 & comply==1, 4,
    ifelse(treat==1 & comply==0, 2,
    ifelse(treat==0 & comply==1, 1,
    ifelse(treat==0 & comply==0, 1, NA)))))

df <- df %>% mutate(treat_effect_d=
  ifelse(treat==1 & comply==1, -1,
  ifelse(treat==1 & comply==0, 2,
  ifelse(treat==0 & comply==1, 3,
  ifelse(treat==0 & comply==0, 3, NA)))))

# Create pre and post outcomes. Here the primary outcome is height-for-age, measured after one year.

df <- df %>% mutate(height=
  ifelse(post==0, 0.15*male+0.25*age+0.38*upper_arm+0.25*educ_mom+0.15*mom_height+0.15*dad_height+rnorm(n()),
  ifelse(post==1, treat_effect_h+height+rnorm(n(),3,.5), height)))

df$height <-rescale(df$height, to = c(26,44))

# Secondary outcome: Weight (measured in pounds) after one year. 
# Do not include variables for parents' height, as they are not good explanatory variables for child's weight. 

df<-df %>% mutate(weight=
  ifelse(post==0, 0.2*male+0.3*age+0.42*upper_arm+0.22*educ_mom+rnorm(n()),
  ifelse(post==1, treat_effect_w+weight+rnorm(n(),.3, .5), weight)))

df$weight <-rescale(df$weight, to = c(15,40))

# Secondary outcome: Diarrhea occurrence (number of diarrhea episodes) after one year.
# Do not include variables for parents' height, as they are not good explanatory variables for child's diarrhea frequency 

df<-df %>% mutate(diarrhea=
  ifelse(post==0, 0.15*male-0.17*age-0.54*upper_arm-0.32*educ_mom+rnorm(n()),
  ifelse(post==1, treat_effect_d+diarrhea+rnorm(n(),.3, .5), diarrhea)))

df$diarrhea <-rescale(df$diarrhea, to = c(0,5))

#Update age variable after 1 year: 

df<-df %>% mutate(age_2=
  ifelse(age==1 & post==1, 2,
  ifelse(age==2 & post==1, 3,
  ifelse(age==3 & post==1, 4,
  ifelse(age==4 & post==1, 5,
  ifelse(age==5 & post==1, 6,age))))))
```

Please refer to this document to see figures and tables if necessary. The following document visualizes the effects of a probiotic yogurt on childrens' height, weight and diarrhea frequency. 

Table 1 below displays the balance table prior to the intervention. The table indicates that there are no statistically significant differences between the treatment group and control group in terms of the variables listed, except for diarrhea occurrence, which is higher in the treatment group than in the control group. This is most likely due to the geographical location of the villages, where some may have access to cleaner drinking water.  

```{r balance table, echo=FALSE, warning=FALSE, comments=FALSE, message=FALSE}
#==============
#Balance Table
#==============
#install.packages("kableExtra")
library(kableExtra)
library(pacman)

#balance table function
{
# here is the function
balance_table_frame <- function(vars, treat_var, data_set) {
  # load packages using pacman (installs package if necessary)
  if (!require(pacman)) install.packages('pacman', repos = 'https://cran.rstudio.com')
  pacman::p_load(broom, haven, knitr, sandwich, data.table, tidyverse) 
  
  # turn off scientific notation except for big numbers
  options(scipen = 9) 
  options(digits=3)
  # function to calculate corrected SEs for OLS regression 
  cse = function(reg) {
    rob = sqrt(diag(vcovHC(reg, type = "HC1")))
    return(rob)
  } 
  n_vars <- length(vars) 
  treat <- rep(treat_var, t=n_vars)
  data <- rep(data_set, t=n_vars) 
  
  coeff <- function(y, x, d) { 
    df <- get(d) 
    reg <- lm(as.formula(paste0(y," ~ ", x)), data=df) 
    n_obs <- summary(reg)$df[2] + 2        # grab the regression sample size
    coef <- tidy(reg) %>% 
      select(term, estimate, std.error)  
    rob_se <- as.data.frame(cse(reg)) %>%           # robust SEs
      rownames_to_column(var = "term") %>% 
      rename(se_robust = `cse(reg)`) 
    treat_est <- coef %>% 
      left_join(rob_se) %>% 
      mutate(treat_var = x,
             variable = y,
             n_obs = n_obs, 
             p_value = 2*pnorm(-abs(estimate/se_robust),0,1)) 
    treat_est <- as.data.frame(treat_est)
    return(treat_est)
  }
  
  # use mapply to get the coefficients and p values 
  qq <- mapply(coeff, vars, treat, data, SIMPLIFY = FALSE) 
  
  # get the data set for table
  qqq <- do.call("rbind",qq)  
  control <- qqq %>% 
    filter(term=="(Intercept)") %>% 
    select(control=estimate, variable)
  balance_table <- qqq %>% 
    filter(term!="(Intercept)")  %>% 
    select(diff=estimate, variable, p_value, n_obs) %>% 
    left_join(control) %>% 
    mutate(treated = control+diff) %>% 
    select(variable, control, treated, diff, p_value, n_obs)
}
# end of function (remember to copy the close brace } above)
}

baltable<-balance_table_frame(c("male","age","diarrhea","educ_mom","height","weight","upper_arm","med_cond","wealth_index", "mom_height","dad_height"),c("treat"),c("df"))

baltable %>% 
  kbl()%>%
  kable_paper("hover", full_width=F)

```

Figures 1-3 display the treatment effect of the probiotic on height. Figures 4-6 do the same for the effect of the probiotic on weight. Figures 7-10 display these effects for diarrhea frequency

```{r graphs1, warning=FALSE, echo=FALSE, comment=FALSE, message=FALSE}
#=========
#Graphs
#=========

#Graphs for HEIGHT. 

#1. Boxplot of height-for-age before and after the intervention.

pre_treat<-subset(df, post=="0" & comply=="1")
pre_treat$treat_f <- as.factor(pre_treat$treat)

ggplot(data=pre_treat, aes(x=treat_f, y=height,fill=treat_f)) +
  geom_boxplot() + 
  labs(title="Figure 1: Height (in inches) Pre-Intervention") + 
  labs(x="Treatment Group", y="Height (in inches) Before Intervention")+
  labs(fill="Treatment Group")+
  scale_fill_discrete(labels=c("0:Control Group (no probiotic)", "1: Treated Group (received probiotic)"))
  
post_treat<-subset(df, post=="1" & comply=="1")
post_treat$treat_f <- as.factor(post_treat$treat)

ggplot(data=post_treat, aes(x=treat_f, y=height, fill=treat_f)) +
  geom_boxplot() + 
  labs(title="Figure 2: Height (in Inches) After Intervention") + 
  labs(x="Treatment Group", y="Height (in inches)")+
  labs(fill="Treatment Group")+
  scale_fill_discrete(labels=c("0: Control Group (no probiotic)", "1: Treatment Group (received probiotic)"))

#2. Linear graph of height (in inches) and age (in years), grouped by treatment.

df$treat_f<- as.factor(df$treat)

ggplot(data=post_treat, aes(x=age_2, y=height, group=treat_f, fill=treat_f))+
  geom_smooth(method=loess, color="black", size=1)+
  labs(title="Figure 3: Height-For-Age Post-Intervention", 
       x="Age (in years)" , y="Height (in inches)")+
  scale_fill_discrete(name="Treatment Group", labels=c("0: Control Group (no probiotic)", "1: Treatement Group (received probiotic)"))

```

Figures 1 and 2: The primary outcome of the study was increase in height (or height-for-age). Results of the study show that there is a causal effect between the consumption of probiotic yogurt in children aged 1-5 years and height. Figures 1 and 2 display the boxplots of height-for-age (measured in inches) before and after the intervention, respectively. Figure 1 displays that pre-intervention, the average height of children in the control group is close to 28.5 inches, and the average height of children in the treatment group is 28.6 inches. Figure 2 displays that post-intervention, the average height of children in the treatment group is slightly higher than those in the control group. In the control group, the average height is now close to 38 inches, while the treatment group has an average of around 40 inches. Thus, this suggests that children who consume one serving of probiotic yogurt daily for one year are likely to be taller than children who do not. 

Figure 3: Next, we will analyze the linear (scatter) plots of the effect of the probiotic on height (post-intervention). Note that the points are excluded from the graph, as they do not display a clear correlation between the variables. Figure 3 illustrates the relationship between age (in years) and height (in inches), where the data is grouped by whether or not the child received the probiotic treatment. The graph indicates that, post-intervention, children in the treatment group are taller than children in the control group. The most notable discrepancy occurs between 4 and 5 years old, where the children in the control group are roughly 38.5 inches at age 4 and the children in the treatment group are 40 inches. Children in the control group grow to 40 inches at age 5, while those in the treatment group grow to 41.5 inches. Similar to the boxplot, this graph confirms the notion that children who consume the probiotic daily for one year are slightly taller than those who do not. However, it is important to note that the duration of the study was only one year, and for future research it may be beneficial to extend the time period of the study to see if these results hold after a few years. 

```{r graphs2, warning=FALSE, echo=FALSE, comment=FALSE, message=FALSE }


#Graphs for WEIGHT

#3. Boxplot of weight-for-age before and after the intervention. 

ggplot(data=pre_treat, aes(x=treat_f, y=weight,fill=treat_f)) +
  geom_boxplot() + 
  labs(title="Figure 4: Weight (in pounds) Pre-Intervention") + 
  labs(x="Treatment Group", y="Weight (in pounds) Before Intervention")+
  labs(fill="Treatment Group")+
  scale_fill_discrete(labels=c("0: Control Group (no probiotic)", "1: Treatment Group (received probiotic)"))

ggplot(data=post_treat, aes(x=treat_f, y=weight,fill=treat_f)) +
  geom_boxplot() + 
  labs(title="Figure 5: Weight (in pounds) After Intervention") + 
  labs(x="Treatment Group", y="Weight (in pounds)")+
  labs(fill="Treatment Group")+
  scale_fill_discrete(labels=c("0: Control Group (no probiotic)", "1: Treatment Group (received probiotic)"))

#4. Linear graph of weight(in pounds) and age (in years)

ggplot(data=post_treat, aes(x=age_2, y=weight, group=treat_f, fill=treat_f))+
  geom_smooth(method=loess, color="black", size=1)+
  labs(title="Figure 6: Weight-For-Age Post-Intervention", 
       x="Age (in years)" , y="Weight (in pounds)")+
  scale_fill_discrete(name="Treatment Group", labels=c("0: Control Group (no probiotic)", "1: Treatement Group (received probiotic)"))

```


Figures 4 and 5: The secondary outcomes in this study are an increase in weight and a reduction in diarrhea occurrence. The results indicate that there is a causal effect between the consumption of probiotic yogurt and weight, as well as probiotic yogurt and diarrhea frequency. The next two figures, Figure 4 and Figure 5, display boxplots of the secondary outcome, weight-for-age (measured in pounds), pre-intervention and post-intervention. Pre-intervention, the plot indicates that the average weight of children in the control group and children in the treatment group is roughly the same, at about 17.5 pounds. Post-intervention, there is a larger discrepancy between the weight of the children in the two groups. In the control group, the average weight has increased to about 30.2 pounds, while the average weight in the treatment group is around 32.5 pounds. This indicates that children who consume one daily serving of yogurt for one year have a heavier weight on average than those who do not. 

Figure 6: Figure 6 visualizes the correlation between age (in years) and weight (in pounds), where again, the data is grouped by treatment. Here it is evident that children in the treatment group weigh more post-intervention than children in the control group. It appears that at every age from 2 years old to 6 years old, children in the treatment group weigh more post-intervention. The difference in weight between the two groups appears to be larger between ages 2 to 3. In the control group, children weigh just over 25 pounds at age 2, while children in the treatment group weigh closer to 27.5 pounds. At age 3, children in the control group are about 27.8 pounds, while children in the treatment group weigh 30 pounds. This reinforces the conclusion that daily consumption of the probiotic yogurt increases weight after one year. 

```{r graphs3, warning=FALSE, echo=FALSE, comment=FALSE, message=FALSE}

#Graphs for DIARRHEA 

#5. Diarrhea occurrence before and after the intervention. 

pre_treat<-subset(df, post=="0" & comply=="1")
pre_treat$treat_f <- as.factor(pre_treat$treat)

ggplot(data=pre_treat, aes(x=treat_f, y=diarrhea,fill=treat_f)) +
  geom_boxplot() + 
  labs(title="Figure 7: Number of Diarrhea Episodes Pre-Intervention") + 
  labs(x="Treatment Group", y="Number of Diarrhea Episodes")+
  labs(fill="Treatment Group")+
  scale_fill_discrete(labels=c("0: Control Group (no probiotic)", "1: Treatment Group (received probiotic)"))

ggplot(data=post_treat, aes(x=treat_f, y=diarrhea,fill=treat_f)) +
  geom_boxplot() + 
  labs(title="Figure 8: Number of Diarrhea Episodes After Intervention") + 
  labs(x="Treatment Group", y="Number of Diarrhea Episodes")+
  labs(fill="Treatment Group")+
  scale_fill_discrete(labels=c("0: Control Group (no probiotic)", "1: Treatment Group (received probiotic)"))

#6. Linear graph of diarrhea occurrence and age.

ggplot(data=post_treat, aes(x=age_2, y=diarrhea, group=treat_f, fill=treat_f))+
  geom_smooth(method=loess, color="black", size=1)+
  labs(title="Figure 9: Diarrhea Occurrence Post-Intervention", 
       x="Age (in years)" , y="Diarrhea Occurrence (Number of Episode)")+
  scale_fill_discrete(name="Treatment Group", labels=c("0: Control Group (no probiotic)", "1: Treatement Group (received probiotic)"))

#7. Radar Graph for Diarrhea

#install.packages("fmsb")
devtools::install_github("ricardo-bion/ggradar", dependencies = TRUE)
#library(fmsb)
library(ggradar)
library(scales)

# Radar graph using ggradar
xx <- df %>% filter(post==1) %>% select(-id,-post, -comply, -treat_effect_h,-treat_effect_w,-treat_effect_d,-village_id,-comply,-weight,-height,-treat_f,-med_cond,-wealth_index,-mom_height,-dad_height) %>% 
  rename(group=treat) %>% mutate(group=as.character(group)) %>% 
  mutate_each(funs(scales::rescale),-group) %>% 
  group_by(group) %>% 
  summarise(across(male:upper_arm, base::mean))
ggradar(xx,label.gridline.min = F, label.gridline.mid = F, label.gridline.max = F)+
  labs(title="Figure 10: Radar graph of diarrhea frequency and control variables") + 
  theme(plot.title = element_text(size=1)+
  theme(plot.title.position = "plot"))


```

Figures 7 and 8: The final two boxplots display the impact of the probiotic yogurt on diarrhea occurrence, which is measured in the number of diarrhea episodes a child experiences. In Figure 7, we see that pre-intervention, the average number of diarrhea episodes in both the control group and the treatment group is around 1.2-1.3. Post-intervention, the number of diarrhea episodes in both groups increased significantly, however the number of episodes experienced was lower in the treatment group than in the control group (see Figure 8). In the control group, the average number of diarrhea episodes is close to 4, while in the treatment group the average number is closer to 3. This suggests that while the probiotic is unlikely to completely prevent diarrhea occurrence in malnourished children, it may at least reduce the number of episodes a child experiences. 

Figure 9: Figure 9 shows the linear plot between age (in years) and diarrhea occurrence (number of episodes experienced). Both groups show a fluctuation in diarrhea frequency as age increases, but it is clear that children in the treatment group experience a lower number of diarrhea episodes than children in the control group, post-intervention. In the control group, most children experience more than 4 episodes of diarrhea during one year, while children in the treatment group experience closer to 2.8-3 episodes of diarrhea in one year. This is in line with related research, as discussed in an earlier section of this paper. 

Figure 10: We also include a radar chart to measure the impact of the probiotic on diarrhea frequency, as it indicates a notable difference between the control and treatment groups (see Figure 10). Clearly, there is a significant decrease in diarrhea frequency in the treatment group post-intervention. We do not include a radar chart for the primary outcome, height, or the secondary outcome, weight, as the extent of the difference between the two groups is not clearly displayed in this format. 

```{r regressions, warning=FALSE, echo=FALSE}

#============
#Regressions
#============

#Height

reg1<-lm(height~post+treat+post*treat, data=df)
reg2<-lm(height~post+treat+post*treat+male, data=df)
reg3<-lm(height~post+treat+post*treat+male+age, data=df)
reg4<-lm(height~post+treat+post*treat+male+age+upper_arm, data=df)
reg5<-lm(height~post+treat+post*treat+male+age+upper_arm+educ_mom, data=df)
reg6<-lm(height~post+treat+post*treat+male+age+upper_arm+educ_mom+mom_height, data=df)
reg7<-lm(height~post+treat+post*treat+male+age+upper_arm+educ_mom+mom_height+dad_height, data=df)

stargazer(reg1, reg2, reg3, reg4,reg5, reg6, reg7,
          se=list(cse(reg1),cse(reg2),cse(reg3),cse(reg4), cse(reg5), cse(reg6), cse(reg7)), 
          title="Table 2: Effect of Control Variables on Height (After 1 Year)", type="text", 
          df=FALSE, digits=3)
#Weight
reg8<-lm(weight~post+treat+post*treat, data=df)
reg9<-lm(weight~post+treat+post*treat+male, data=df)
reg10<-lm(weight~post+treat+post*treat+male+age, data=df)
reg11<-lm(weight~post+treat+post*treat+male+age+upper_arm, data=df)
reg12<-lm(weight~post+treat+post*treat+male+age+upper_arm+educ_mom, data=df)

stargazer(reg8, reg9, reg10, reg11, reg12,
          se=list(cse(reg8),cse(reg9),cse(reg10),cse(reg11),cse(reg12)), 
          title="Table 3: Effect of Control Variables on Weight (After 1 Year)", type="text", 
          df=FALSE, digits=3)

#Diarrhea Frequency

reg13<-lm(diarrhea~post+treat+post*treat, data=df)
reg14<-lm(diarrhea~post+treat+post*treat+male, data=df)
reg15<-lm(diarrhea~post+treat+post*treat+male+age, data=df)
reg16<-lm(diarrhea~post+treat+post*treat+male+age+upper_arm, data=df)
reg17<-lm(diarrhea~post+treat+post*treat+male+age+upper_arm+educ_mom, data=df)

stargazer(reg13, reg14, reg15, reg16, reg17,
          se=list(cse(reg13), cse(reg14),cse(reg15),cse(reg16), cse(reg17)), 
          title="Table 4: Effect of Control Variables on Weight (After 1 Year)", type="text", 
          df=FALSE, digits=3)

```


In this study, there are three different sets of regressions, one for each outcome variable. Note that in our baseline specifications, we do not include the variables for existing medical conditions (med_cond) or wealth index (wealth_index) as regressors. We address this in the following section of the paper. In the first set of regressions, the dependent variable is height (or height-for-age) in inches, which is the primary outcome. In these regressions, we include the interaction term for “post” and “treat”, which indicates that the effect of pre- or post- treatment on height depends on whether or not a child received the probiotic treatment. Table 2 displays regression results where height is the dependent variable. Column 1 indicates that if a child receives the probiotic treatment, then their height increases by 0.864 inches after one year. This value is statistically significant at all levels and across all regressions. In column 2, the control variable for gender is added to the regression, and indicates that if a child is male, then they are taller than females by 0.097 inches. Note that this term is not statistically significant, and remains insignificant across all five regressions. This suggests that gender most likely does not have an effect on height-for-age in this study. In column 3, the variable for age is added to the regression, and has a statistically significant coefficient of 1.170. Thus, an increase in age by 1 year increases height by 1.170 inches. Column 4 adds the variable for malnutrition, “upper_arm”. The coefficient on this variable is also statistically significant, at 0.078. This implies that as the circumference of a child’s upper-arm increases by 1 inch, their height will increase by 0.078 inches. It is also important to note that when this variable is added to the regression, the coefficient on age decreases to 1.120, implying that the third regression slightly overestimates the effect of age on height. Column 5 includes the variable for how many years of education a child’s mom has experienced. The coefficient on this term is 0.090, indicating that if the child’s mother has a primary school education, their height-for-age is likely to increase by 0.090 inches. It is statistically significant at all levels, and when added, the coefficient for malnutrition (upper_arm) decreases by 0.01. The last two variables we add are the explanatory variables for each parent’s height. In column 6, the coefficient for the mother’s height is 0.042, indicating that for every 1 inch increase in mother’s height,  there is an increase in the child’s height by 0.042 inches. Column 7 includes the coefficient for father’s height, 0.039, implying that for every 1 inch increase in height, there is an increase in the child’s height, there is a 0.039 increase in height in the child. Essentially, if the parents are taller, there is a higher likelihood of the child being taller. 

The next five regressions in Table 3 have weight (measured in pounds) as the dependent variable. Similar to the previous regressions, Column 1 displays the coefficient on the interaction term as 1.630, indicating that when a child receives the treatment, their weight increases by 1.630 pounds. This value is statistically significant at all three levels. In column 2, the control variable for gender is added to the regression. The variable has a coefficient of -0.030, indicating that if a child is male, they weigh 0.03 pounds less than females. This term is not statistically significant, and remains insignificant across the remaining regressions. Column 3 adds the variable for age to the regression, which has a value of 1.410 and is statistically significant at all levels. This implies that as age increases by one year, weight increases by around 1.41 pounds. In column 4, the variable for malnutrition is added, and has a coefficient of 0.133, implying that if upper-arm circumference increases by 1 inch, weight increases by 0.133 pounds. This term is statistically significant, and we note that when added to the regression, the coefficient on age decreases to 1.310. Thus, in column 3, the coefficient for age is an overestimate. Column 5 adds the variable for mother’s education (years), which has a statistically significant coefficient of 0.059, so if the mother’s education increases by 1 year, the child’s weight increases by 0.059 pounds. Note that we do not include the variables for each parents’ height in this set of regressions or the next, as we do not consider them explanatory variables for a child’s height or diarrhea occurrence. 
	
The last set of regressions contain diarrhea occurrence (measured in the number of diarrhea episodes per year) as the dependent variable. Similar to the previous sets of regressions, column 1 indicates that if a child is in the treatment group, then the number of episodes of diarrhea they experience decreases by 0.966 days. Column 2 adds the control variable for gender to the regression, which has a coefficient of 0.001, implying that if a child is male, the number of episodes of diarrhea they experience increases by 0.001 days. Again, this value is not statistically significant. In column 3, age is included in the regression, and indicates that as a child’s age increases by 1 year, the number of diarrhea episodes they experience decreases by 0.069. In the next column, the variable for malnutrition is added to the regression, and it has a coefficient of -0.078, implying that as a child’s upper-arm circumference increases by 1 inch, the number of diarrhea episodes they experience per year decreases by 0.078. Again, this value is statistically significant. The coefficient for age increases to -0.010 in this column and is not statistically significant in this column, but decreases to -0.014 in the final regression where it is statistically significant again. Column 5 includes the variable for mother’s education (in years), which has a statistically significant coefficient of -0.033. Thus, when the number of years of education a mother experiences increases by 1, then the frequency of diarrhea decreases by 0.033. 











```{r robustness, warning=FALSE, echo=FALSE}

#===========
#Robustness
#===========

#Change Model Specifications 

#1. Alternate Specification: control for existing medical conditions.  

df <- df %>% mutate(height2=
  ifelse(post==0, 0.15*male+0.25*age+0.38*upper_arm+0.25*educ_mom+0.15*mom_height+0.15*dad_height+0.12*med_cond+rnorm(n()),
  ifelse(post==1, treat_effect_h+height+rnorm(n(),3,.5), height)))

df$height2<-rescale(df$height, to = c(26,44))

reg18<-lm(height2~post+treat+post*treat, data=df)
reg19<-lm(height2~post+treat+post*treat+male, data=df)
reg20<-lm(height2~post+treat+post*treat+male+age, data=df)
reg21<-lm(height2~post+treat+post*treat+male+age+upper_arm, data=df)
reg22<-lm(height2~post+treat+post*treat+male+age+upper_arm+educ_mom, data=df)
reg23<-lm(height2~post+treat+post*treat+male+age+upper_arm+educ_mom+med_cond, data=df)
reg24<-lm(height2~post+treat+post*treat+male+age+upper_arm+educ_mom+med_cond+mom_height, data=df)
reg25<-lm(height2~post+treat+post*treat+male+age+upper_arm+educ_mom+med_cond+mom_height+dad_height, data=df)


stargazer(reg18, reg19, reg20, reg21, reg22, reg23, reg24, reg25,
          se=list(cse(reg18),cse(reg19),cse(reg20),cse(reg21),cse(reg22),cse(reg24),cse(reg25)), 
          title="Table 5: Effect of Control Variables on Height (After 1 Year)", type="text", 
          df=FALSE, digits=3)

#2. Include a control variable for wealth index.

df <- df %>% mutate(height3=
  ifelse(post==0, 0.15*male+0.25*age+0.38*upper_arm+0.25*educ_mom+0.15*mom_height+0.15*dad_height+0.12*med_cond+0.15*wealth_index+rnorm(n()),
  ifelse(post==1, treat_effect_h+height+rnorm(n(),3,.5), height)))

df$height3<-rescale(df$height3, to = c(26,44))

reg26<-lm(height3~post+treat+post*treat, data=df)
reg27<-lm(height3~post+treat+post*treat+age, data=df)
reg28<-lm(height3~post+treat+post*treat+age+upper_arm, data=df)
reg29<-lm(height3~post+treat+post*treat+age+upper_arm+educ_mom, data=df)
reg30<-lm(height3~post+treat+post*treat+age+upper_arm+educ_mom+mom_height, data=df)
reg31<-lm(height3~post+treat+post*treat+age+upper_arm+educ_mom+mom_height+dad_height, data=df)
reg32<-lm(height3~post+treat+post*treat+age+upper_arm+educ_mom+mom_height+dad_height+wealth_index, data=df)

stargazer(reg26, reg27, reg28, reg29, reg30, reg31, reg32,
          se=list(cse(reg26),cse(reg27),cse(reg28),cse(reg29), cse(reg30), cse(reg31), cse(reg32)), 
          title="Table 6: Effect of Control Variables on Height (After 1 Year)", type="text", 
          df=FALSE, digits=3)



#DD table check 
#pre_treat2<-subset(pre_treat, treat=="1")
#mean(pre_treat2$diarrhea)

#post_treat2<-subset(post_treat, treat=="1")
#mean(post_treat2$diarrhea)
```


This study includes multiple outcomes, so rather than testing the effect of the treatment on a new outcome in order to perform a robustness check, we will simply modify the regressions for the primary outcome variable, height. The base specification of our first set of regressions includes the causal variable of interest (the effect of the probiotic treatment) and plausible control variable that may influence the primary outcome. In our alternate specification, we will now include a variable that controls for any existing medical conditions a child may have. We include this variable as a binomial variable that takes the value 0 if a child has no known existing medical conditions, and 1 if a child does have existing medical conditions. We choose to include this variable, as it may be correlated with regressors such as upper-arm circumference, as well as the outcome variable, height. Not including this variable may have resulted in omitted variable bias in our original baseline specification. When we perform the regression analysis, we find that controlling for existing medical conditions does not change the baseline specification. Table 5 displays these values, and when comparing to Table 2, we can see that the estimates of the coefficients of interest are numerically similar to the baseline specification in the alternate specification. Additionally, we see that the coefficient for existing medical conditions is not statistically significant. In another alternate specification, we include the regressor for wealth_index, as it was not included in our baseline specification regressions, and we keep height as our dependent variable (see Table 6). Here we find that the coefficient of wealth index is statistically significant, so it may have been beneficial to include it as a regressor in our baseline specifications. However, the values on the coefficients of interest do not vary significantly. Thus, our alternate specifications suggest that the results from our baseline specification are reliable. In the future, we could also drop the regressor for gender, as it is not statistically significant, so its inclusion is not necessary in the regression analysis. We would assume that dropping this regressor would not change the values of the coefficients of interest (significantly). 













